A methodology for calculating active force-time functions from broadband piezoelectric sensors

### 2020-05-01 Article_file_Source_reconstruction.tex
Updates from Overleaf

Figure \ref{fig1}(a) shows a schematic representations of the steel platen (350 mm $\times$ 350 mm $\times$ 50 mm) in the extruded aluminium frame. Small rubber pads (10 mm $\times$ 10 mm $\times$ 1 mm) are used to base isolate the steel platen from the frame. Material properties of the steel plate required to model the wave propagation problem in the steel plate are given in Table \ref{table1}. Centrally located on the top surface is a piezoelectric actuator built in-house.  This sensor is connected to an high-voltage pulsing unit (HVP, Elsys Instruments AE-HV-MUX). This unit consist of a PiezosystemJena voltage amplifier for pulse generation (HVP 1000/200) that is fully integrated with the data acquisition (DAQ) software (Elsys Instruments TraNET). Figure \ref{fig1}(c) shows the circuit diagram of the HPV that is used to deliver an amplified voltage pulse to the piezoelectric actuator. The pulse and discharge of the system is depicted in the Figure \ref{fig1}(d). The time-dependent change in voltage when the switch position is in ``pulse'' (state 1) is given as:

@@

\noindent where $R_{2}$ = 1000 $\Omega$, $C_{eq}$ is the equivalent capacitance of $C_{PZT}$ and $C_{0}$ in series using electrostatic theory.  Figure \ref{fig1}(b) show the array holder for the passive sensor (KRNBB-PC) which are used to measure the stress waves produced by the active piezoelectric source. The aluminium array had a 7 $\times$ 7 locations with 23 mm spacing in both the $x$- and $y-$ directions.  In this study, we have assumed our source is symmetric about the $1-3$ and $2-3$ planes (i.e. aligned in the $3$-direction) and, therefore, have focused most of our sensors converge to one quadrant.  Similar colors of the sensors locations in Figure \ref{fig1}(b), represents similar epicentral locations.  We have redundant measurements at all epicentral locations expect $x$ = 0 mm, 33 mm and 96 mm and have shown that there appear to be little to no directivity in the active source.

A total of 13 sensor are used and the spectral characteristics of these sensors have been well examined in the literature using the absolute calibration methods \citep{Glaser1998, McLaskey2010, McLaskey2012, Selvadurai2015, Selvadurai2019, Wu}. \citet{Glaser1998} provides a detailed account to sensor attributes used by KRN Services, including a the small field emission transistor (FET)-based Sanyo (2SK715W) preamplifier internal to the sensor casing to improve impedance matching.  These sensors have shown flat displacements-responses between 100 kHz to 1 MHz \citep{McLaskey2012, Selvadurai2019}.  At longer wavelengths between 1 kHz to 50 kHz these sensors have been found to behave more like accelerometer \citep{Wu}.

@@

We build on the recent studies of signal analysis and instrument calibration by \citet{McLaskey2012} continuing this analysis using Green's function formalization \citep{Aki2002, Johnson1974}. Due to spatial reciprocity of the representation theorem \citep{Aki2002} and the invariant nature of the seismic wave equation to time-reversed solutions \citep{Fink1992}, we can use convolution of the components highlighted in Figure \ref{fig2} to analyze our system in a linear time-invariant (LTI) fashion. This assumes that changes in the sensor and source behavior and material properties are unaffected over time.  We assume point representations of both the sensor and source location, which might be influenced so-called ``aperture'' effect. However, this is minimized by using the point contact conical PZT crystal, which will be discussed later when we examine in more detail how the force systems of passive and active PZT sensors.

Using the classical theory describing dynamic elasticity \citep{Aki2002}, we can use Green's functions to relate the displacement $u$ at a known location $\mathbf{x}$ and time $t$ to a force $f$ at another point $\mathbf{\xi}$ and time $\tau$. This is given as the convolution of the force with the Green's function

@@

\noindent We note that $\ast$ represents convolution in the time domain, $f$ is the force acting in the $j$ direction at location $\mathbf{\xi}$ and $g_{kj}\left( \mathbf{x}, t;\mathbf{\xi}, \tau \right)$ is the elastodynamic Green's function describing the displacement $u$ in the direction $k$ at location $\mathbf{x}$. For the elastodynamic solutions studied here, we assume that convolution $\ast$ is applicable since the system in question are linear time-invariant (LTI) and that convolution has commutativity, associative and distributive properties. The true Green's function is the displacement field for the unit impulse force $\delta_{j}$ or the identity convolution.

>>>>

Figure \ref{fig1}(a) shows a schematic representations of the steel platen (350 mm $\times$ 350 mm $\times$ 50 mm) in the extruded aluminium frame. Small rubber pads (5 mm $\times$ 5 mm $\times$ 1 mm) are used to base isolate the steel platen from the frame. Material properties of the steel plate required to model the wave propagation problem are given in Table \ref{table1}. Centrally located on the top surface is a piezoelectric actuator built in-house.  This sensor is connected to an high-voltage pulsing unit (HVP, Elsys Instruments AE-HV-MUX). This unit consist of a PiezosystemJena voltage amplifier for pulse generation (HVP 1000/200) that is fully integrated with the data acquisition (DAQ) software (Elsys Instruments TraNET). Figure \ref{fig1}(c) shows the circuit diagram of the HPV that is used to deliver an amplified voltage pulse to the piezoelectric actuator. The pulse and discharge of the system is depicted in the Figure \ref{fig1}(d). The time-dependent change in voltage when the switch position is in ``pulse'' (state 1) is given as:

@@

\noindent where $R_{2}$ = 1000 $\Omega$, $C_{eq}$ is the equivalent capacitance of $C_{PZT}$ and $C_{0}$ in series using electrostatic theory.

Figure \ref{fig1}(b) show the array holder for the passive PZT sensor (KRN Services model: KRNBB-PC) which are used to measure the stress waves produced by the active piezoelectric source. The aluminium array had a 7 $\times$ 7 locations with 23 mm spacing in both the $1$- and $2$-directions.  In this study, we have assumed our source is symmetric about the $1-3$ and $2-3$ planes (i.e. aligned in the $3$-direction) and, therefore, have focused most of our passive sensors converge to one quadrant of the array holder.  Similar colors of the sensors locations in Figure \ref{fig1}(b), represents their epicentral locations.  We have redundant measurements at all epicentral locations expect $x$ = 0 mm, 33 mm and 96 mm and we show in Section \ref{results} that there appears to be little to no misalignment of the active source.

A total of 13 sensor are used and the spectral characteristics of these sensors have been well examined in the literature using the absolute calibration methods \citep{Glaser1998, McLaskey2010, McLaskey2012, Selvadurai2015, Selvadurai2019, Wu}. \citet{Glaser1998} provides a detailed account to sensor attributes. This sensor includes a the small field emission transistor (FET)-based (Sanyo model: 2SK715W) that preamplifies internally to improve impedance matching and loss due to wire capacitance.  These sensors have shown flat displacements-responses between 100 kHz to 1 MHz \citep{McLaskey2012, Selvadurai2019}.  At longer wavelengths between 1 kHz to 50 kHz these sensors have been found to behave more similar to an accelerometer \citep{Wu}.

@@

We build on the recent studies of signal analysis and instrument calibration by \citet{McLaskey2012} and continuing our analysis using Green's function formalization \citep{Aki2002, Johnson1974}. Due to spatial reciprocity of the representation theorem \citep{Aki2002} and the invariant nature of the seismic wave equation to time-reversed solutions \citep{Fink1992}, we can use convolution of the components highlighted in Figure \ref{fig2} to analyze our linear time-invariant (LTI) system. This approach assumes that changes in the sensor and source behavior and material properties are unaffected over time.  We assume point representations at both the sensor and source location, which might be influenced so-called ``aperture'' effect. However, this is minimized by using a smaller contact point characteristic of the conical frustum PZT crystal, which will be discussed later when we examine in more detail how the force systems of the PZT actuator.

Using the classical theory describing dynamic elasticity \citep{Aki2002}, we use Green's functions to relate the displacement $u$ at a known location $\mathbf{x}$ and time $t$ to a force $f$ at another point $\mathbf{\xi}$ and time $\tau$. This is given as the convolution of the force with the Green's function

@@

\noindent We note that $\ast$ represents convolution in the time domain, subscripts reflect Einstein summation convention, $f$ is the force acting in the $j$ direction at location $\mathbf{\xi}$ and $g_{kj}\left( \mathbf{x}, t;\mathbf{\xi}, \tau \right)$ is the elastodynamic Green's function describing the displacement $u$ in the direction $k$ at location $\mathbf{x}$. For the elastodynamic solutions studied here, we assume that convolution $\ast$ is applicable since the system in question are linear time-invariant (LTI) and that convolution has commutativity, associative and distributive properties. The true Green's function is the displacement field for the unit impulse force $\delta_{j}$ or the identity convolution.
